%This file makes a vita page in the required two column format.
\begin{center}
            VITA
\end{center}
\begin{flushleft}
\begin{tabular}{ll}
2006-2009        &  A.S., Linn-Benton Community College, Albany, Oregon
\\
& \\
2009-2012        &  B.S., University of Oregon, Eugene, Oregon
\\
& \\
2012-2015        &  M.S., New Mexico State University, Las Cruces, New Mexico
\end{tabular}
\end{flushleft}
\vspace{0.1in}
\begin{center}PUBLICATIONS
\end{center}
  C. Adams \textit{at al.}, "A Deep Neural Network for Pixel-Level Electromagnetic Particle Identification in the MicroBooNE Liquid Argon Time Projection Chamber”," \textit{Submitted to: Phys. Rev. D}, 2018. \\
  C. Adams \textit{at al.}, "Comparison of Muon-Neutrino-Argon Multiplicity Distributions Observed by MicroBooNE to GENIE Model Predictions," \textit{Submitted to: Phys. Rev. D}, 2018. \\
  C. Adams \textit{at al.}, "Ionization Electron Signal Processing in Single Phase LAr TPCs II: Data/Simulation Comparison and Performance in MicroBooNE," \textit{JINST}, vol. 13, no. 07, p. P07007, 2018. \\
  C. Adams \textit{at al.}, "Ionization Electron Signal Processing in Single Phase LAr TPCs I: Algorithm Description and Quantitative Evaluation with MicroBooNE Simulation," \textit{JINST}, vol. 13, no. 07, p. P07006, 2018. \\
  R. Acciarri \textit{at al.}, "The Pandora Multi-Algorithm Approach to Automated Pattern Recognition of Cosmic Ray Muon and Neutrino Events in the MicroBooNE Detector," \textit{Eur. Phys. J.}, vol. C78, p. 82, 2018. \\
  R. Acciarri \textit{at al.}, "Measurement of Cosmic Ray Reconstruction Efficiencies in the MicroBooNE LAr TPC Using a Small External Cosmic Ray Counter," \textit{JINST}, vol. 12, no. 12, p. P12030, 2017. \\
  R. Acciarri \textit{at al.}, "Noise Characterization and Filtering in the MicroBooNE Liquid Argon TPC," \textit{JINST}, vol. 12, no. 08, p. P08003, 2017. \\
  R. Acciarri \textit{at al.}, "Michel Electron Reconstruction Using Cosmic-Ray Data from the MicroBooNE LArTPC," \textit{JINST}, vol. 12, no. 09, p. P09014, 2017. \\
  P. Abratenko \textit{at al.}, "Determination of Muon Momentum in the MicroBooNE LArTPC Using an Improved Model of Multiple Coulomb Scattering," \textit{JINST}, vol. 12, no. 10, p. P10010, 2017. \\
  R. Acciarri \textit{at al.}, "Convolutional Neural Networks Applied to Neutrino Events in a Liquid Argon Time Projection Chamber," \textit{JINST}, vol. 12, no. 03, p. P03011, 2017. \\
   R. Acciarri \textit{et al.}, "Design and Construction of the MicroBooNE Detector," \textit{JINST}, vol. 12, no. 02, p. P02017, 2017. \\
\begin{center}
FIELD OF STUDY
\end{center}
\begin{flushleft}
Major Field: Experimental Particle Physics
\end{flushleft}

\newpage
%This is the end of the vita page.
